\documentclass[a4paper,10pt]{article}

\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{changepage}

% ---------- PAGE MARGINS ----------
\geometry{
    left=0.6in,
    right=0.6in,
    top=0.6in,
    bottom=0.6in
}

% ---------- GLOBAL FONT SIZE ----------
\renewcommand{\normalsize}{\fontsize{9}{11}\selectfont}

% ---------- SECTION FORMATTING ----------
\titleformat{\section}{\large\scshape}{}{0em}{}[\vspace{0.2em}\titlerule]
\titlespacing{\section}{0pt}{0.6em}{0.3em}

% ---------- SPACING ----------
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlist[itemize]{noitemsep, topsep=0pt, parsep=0pt, partopsep=0pt}
\linespread{1.15}

% ---------- HYPERLINK COLORS ----------
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=blue
}

% ---------- PROJECT COMMAND ----------
\newcommand{\Project}[3]{%
    \noindent \href{#2}{\textbf{#1}} \textbar~\textit{#3}%
    \vspace{0.2em}%
}

% ---------- SUBTITLE COMMAND ----------
\newcommand{\Subtitle}[2][true]{%
    \vspace{0.3em}%
    {\fontsize{10.5}{12}\selectfont \textbf{#2}}%
    \ifstrequal{#1}{true}{\vspace{0.3em}}{}%
}


\begin{document}

% ---------- HEADER ----------
\begin{center}
    {\fontsize{22}{24}\selectfont \textbf{Ali Guliyev}} \\[3pt]
    \href{https://aligu.me/}{Portfolio Website} $|$
    \href{mailto:ali.guliyevoo7@gmail.com}{ali.guliyevoo7@gmail.com} $|$
    \href{https://github.com/aligu7}{Github} $|$
    \href{https://www.linkedin.com/in/ali-guliyev-bb7211219/}{LinkedIn}
\end{center}

% ---------- EDUCATION ----------
\vspace{-1.3em}
\section*{Education}
\begin{adjustwidth}{0.4cm}{0pt}

\Subtitle[false]{ABC Horizon Istanbul} \hfill Sep 2024 -- Jan 2026 \\
\textit{Higher National Diploma (HND) in Computing}

\Subtitle[false]{Wimbledon School of English} \hfill 12 Jun 2023 -- 07 Jul 2023 \\
\textit{Academic IELTS Express (20 hours/week, B2+ Level)}

\end{adjustwidth}

% ---------- TECHNICAL SKILLS ----------
\section*{Technical Skills}
\begin{adjustwidth}{0.4cm}{0pt}
\setlength{\tabcolsep}{1pt} % default is 6pt, reduce as needed
\begin{tabular}{l l}
\textbf{Frontend / Fullstack:} & Nuxt 4, Vue 3, TypeScript, JavaScript, Firebase \\
\textbf{Programming:} & Python, C++ \\
\textbf{Tools \& Ecosystem:} & Linux, Git, Pinia, Vite, Vitest, Cloudflare Pages, Nuxthub, Netlify \\
\end{tabular}
\end{adjustwidth}

% ---------- EXPERIENCE ----------
\section*{Experience}
\begin{adjustwidth}{0.4cm}{0pt}

\Subtitle[false]{Web Developer, Optimax Software} \hfill June 2023 -- Present \\
\href{https://optimaxsoftware.com/}{optimaxsoftware.com}
\begin{itemize}
    \item Built multiple production websites and web apps using Vue 3, Nuxt 4, Pinia, and TypeScript.
    \item Implemented responsive, component-based interfaces with SSR and efficient state management.
    \item Integrated REST APIs and dynamic content for 5k+ monthly users.
    \item Optimised performance, SEO, and accessibility across projects.
\end{itemize}

\Subtitle[false]{Web Developer, 57Colleges} \hfill June 2022 -- August 2023 \\
\href{https://57colleges.com}{57colleges.com}
\begin{itemize}
    \item Developed and optimised responsive web apps using WordPress, HTML, CSS, JavaScript, and Bootstrap.
    \item Implemented full-stack solutions with ASP.NET Core MVC for secure dynamic content.
    \item Collaborated with cross-functional teams to deliver projects on time and improve user engagement.
\end{itemize}

\end{adjustwidth}

% ---------- PROJECTS ----------
\section*{Projects}
\begin{adjustwidth}{0.4cm}{0pt}

% ----- Optimax Software Projects -----
\Subtitle{Optimax Software (Internship Projects):}

\Project{Lama Trader — Next-Generation Trading Platform (Alpha)}{https://lamatrader.com}{Nuxt 4, Vue 3, TypeScript, Pinia, Alpaca API, AG Grid, Dockview, TailwindCSS}
\begin{itemize}
    \item Developed a professional-grade trading platform with multi-widget dashboards and real-time financial data.
    \item Integrated Alpaca API for secure trading and account management.
    \item Built responsive interfaces with Nuxt 4, Vue 3, Pinia, and TypeScript.
    \item Implemented real-time analytics and portfolio dashboards with AG Grid and custom visualizations.
\end{itemize}

\Project{Visual Quran — Data Visualisation Platform}{https://visual.koran.center}{Nuxt 4, Vue 3, TypeScript, UnoCSS, Chart.js, Unovis, anime.js}
\begin{itemize}
    \item Interactive Quran visualisation platform presenting charts, maps, and network graphs.
    \item Leveraged structured datasets and Quran Meta API for scalable data insights.
    \item Implemented SEO optimisation, automated testing (Vitest), and type-safe schema validation (Zod).
\end{itemize}

\Project{Cinoteka — Movie Library Platform}{https://cinoteka.com}{Nuxt 4, TypeScript, Pinia, Drizzle ORM, Cloudflare Pages}
\begin{itemize}
    \item Full-stack movie collection web app with authentication.
    \item Built metadata matching, duplicate detection, and privacy-first design for local media files.
    \item Deployed to Cloudflare Pages with secure state management and persistent user data.
\end{itemize}

\Project{Sozler.im — Quote Sharing Platform}{https://www.sozler.im}{Vue 3, TypeScript, UnoCSS}
\begin{itemize}
    \item Responsive quote-sharing platform with scalable component architecture.
    \item Collaborated on feature development and performance optimisation for enhanced UX.
\end{itemize}

\vspace{1em}
\Subtitle{Other Projects:}

\Project{Dr. Andrews Plastic Surgery — Simulation Tool}{https://github.com/aligu7/daps_simulation}{Nuxt 4, Vue 3, UnoCSS, Firebase}
\begin{itemize}
    \item Interactive simulation tool for plastic surgery practice focusing on secure data handling.
    \item Implemented real-time visualisations, improving patient engagement and workflow.
\end{itemize}

\Project{Post-App — Social Networking Application}{https://postapp-v1.web.app/}{Vue 3, Firebase, UnoCSS}
\begin{itemize}
    \item Full-stack social networking application with real-time updates and dynamic content.
    \item Integrated secure user authentication and intuitive UI components for better engagement.
\end{itemize}

\Project{Vagif Guliyev's Website — Personal Portfolio}{https://guliyev.com}{Nuxt 4, Vue 3, Nuxt Content CMS}
\begin{itemize}
    \item Dynamic personal portfolio website with responsive design and SEO optimisations.
    \item Showcases projects and interactive features for personal branding.
\end{itemize}
\end{adjustwidth}

\section*{Testimonials}
\begin{adjustwidth}{0.4cm}{0pt}
\href{https://www.linkedin.com/in/ali-guliyev-bb7211219/details/recommendations/}{My LinkedIn Recommendations:}
\begin{itemize}
    \item \textit{”To work with Ali for our Iowa plastic surgery practice has been an absolute game-changer. We needed a robust full-stack website that would articulate all of our services and offer a safe and convenient way for our patients to engage with them. Ali did all this and much more within just two weeks!...”}
    
    \hfill \textit{— Aidan Andrews, MS Computer Science Candidate, Entrepreneur and Researcher at UIUC}
\end{itemize}
\end{adjustwidth}

% ---------- CERTIFICATIONS ----------
\section*{Certifications}
\begin{adjustwidth}{0.4cm}{0pt}
\textbf{IELTS – Overall Band Score: 7.0} \hfill British Council (23 Aug 2023)
\end{adjustwidth}

% ---------- LANGUAGES ----------
\section*{Languages}
\begin{adjustwidth}{0.3cm}{0pt}
\begin{tabular}{ll}
\textbullet~\textbf{English}: Fluent & \textbullet~\textbf{Russian}: Native \\
\textbullet~\textbf{Azerbaijani}: Native & \textbullet~\textbf{Turkish}: Native \\
\end{tabular}
\end{adjustwidth}

% ---------- ADDITIONAL INFORMATION ----------
\section*{Additional Information}
\begin{adjustwidth}{0.4cm}{0pt}
Driving Licence – Categories B, B1 (Azerbaijan)
\end{adjustwidth}

\end{document}
